---
title: "Q1"
author: "Huiyan Li"
date: "4/18/2020"
output: html_document
---

# Assignment 2: Question 1

### A) Suppose we decide to collect 30 observations (n = 30). Calculate Power of this test.
```{r}
n = 30
sigma_square = 16
sigma = sqrt(sigma_square)
alpha = 0.05
mu_null = 5
mu_alpha = 4
significance = alpha
```

$Z_0 = \frac{\overline{X} - \mu_0}{\sigma / \sqrt{n}}$ \
$\overline{X} = Z_{\alpha} * \sigma / \sqrt{n} + \mu_0$ \
$\overline{X} = Z_{0.05} * (4 / \sqrt{30}) + 5$ \
$\overline{X} = -1.644854 * 0.73029674334 + 5$ \
$\overline{X} = 3.79876848$ \
$Power = P[\overline{X} \lt 3.79876848$ Under the $H_{\alpha}]$ \

$P[Z \le \frac{\overline{X} - \mu_{\alpha}}{\sigma / \sqrt{n}}] = 1 - P[Z \gt \frac{3.79876848 - 4}{4/\sqrt{30}}] = 1 - pnorm(-0.27554760696) = 1 - 0.3914478 = 0.6085521$ \
$Power = 0.6085521$ \
```{r}
sigma = sqrt(sigma_square)
x_bar = qnorm(significance) * (sigma / sqrt(n)) + mu_null
probability = (x_bar - mu_alpha) / (sigma / sqrt(n))
power = 1 - pnorm(probability)
power
```


### 1.B) Suppose we want to ensure that the power is 80%. What should be the sample size? (n=?)
- $P = \frac{\overline{X} - \mu_0}{\sigma / \sqrt{n}}$ 
- $n = (\frac{p * \sigma}{\overline{X} - \mu_\alpha})^2 = (\frac{qnorm(1 - 0.8)*4}{3.79876848-4})^2 = (16.72941)^2 = 279.8732$ 
```{r}
power = 0.8
reverse_probability = qnorm(1 - 0.8)
estimated_n = ((reverse_probability * sigma)/ (x_bar - mu_alpha))**2
estimated_n
```




















