---
title: "Q2"
author: "Huiyan Li"
date: "4/18/2020"
output: html_document
---

# Assignment 2: Question 2
- For both part of the question, given we don't know the exact vaule for $\sigma$, therefore, we will replace $Z_{\alpha/2}$ with $T_{\alpha/2, df}$ to approximate \
```{r}
# Only change this following line, remove 261 and put your student id
student_id=1001145664
# do not change anything below
set.seed(student_id)
Group1= round(rnorm(15,mean=10,sd=4),2)
Group2= round(rnorm(12,mean=7,sd=4),2)
```

```{r}
group1Size = length(Group1)
group2Size = length(Group2)

group1Mean = mean(Group1)
group2Mean = mean(Group2)

group1Var = var(Group1)
group2Var = var(Group2)

group1SD = sqrt(group1Var)
group2SD = sqrt(group2Var)
```

## A) Assuming $\sigma_{1}^{2} = \sigma_{2}^{2}$ 
### i) Construct a 95% confidence interval for $\mu_1 - \mu_2$ and interpret \
- Given $\sigma_{1}^{2} = \sigma_{2}^{2}$, therefore, $df = n + m - 2 = 15 + 12 - 2 = 25$ 
- Below is the Lower and Upper Confidence Limits equation for equal-variance:
- $P(\overline{X} - \overline{Y} - Z_{\alpha/2} \sqrt{\frac{(m - 1)\sigma_1^2 + (n - 1)\sigma_2^2}{m + n - 2}(\frac{1}{m}+\frac{1}{n})} \lt \mu_1 - \mu_2 \lt \overline{Y} + Z_{\alpha/2} \sqrt{\frac{(m - 1)\sigma_1^2 + (n - 1)\sigma_2^2}{m + n - 2})(\frac{1}{m}+\frac{1}{n})})$ 
- $\mu_1 - \mu_2 = \overline{X} - \overline{Y} \pm t_{1-\alpha/2,df} \sqrt{\frac{(m - 1)\sigma_1^2 + (n - 1)\sigma_2^2}{m + n - 2}(\frac{1}{m}+\frac{1}{n})}$ \
- $\mu_1 - \mu_2 = 10.26933 - 4.41 \pm -2.059539 \sqrt{\frac{(15 - 1)11.46239 + (12 - 1)29.94576}{15 + 12 - 2}(\frac{1}{15}+\frac{1}{12})}$ 
- $\mu_1 - \mu_2 = (2.328404, 9.390263)$ 

```{r}
alpha = 0.05 / 2
dfSize = group1Size + group2Size - 2

lower = group1Mean - group2Mean + qt(alpha,df=dfSize) * sqrt(((((group1Size - 1) * group1Var) + ((group2Size - 1) * group2Var)) /(group1Size + group2Size - 2)) * ((1/group1Size) + (1/group2Size)))
upper = group1Mean - group2Mean - qt(alpha,df=dfSize) * sqrt(((((group1Size - 1) * group1Var) + ((group2Size - 1) * group2Var)) /(group1Size + group2Size - 2)) * ((1/group1Size) + (1/group2Size)))

#t.test(Group1, Group2, var.equal=TRUE) # t.test by default assume the variances are not equal

lower
upper

```
- From this, we can see that  $2.328404 \lt \mu_1 - \mu_2 \lt 9.390263$ 
- Therefore, we are highly confident that the true population from group 1 exceeds the true population from group2 by between 2.328404 - 9.390263.

### ii) At 5% level of significance, test $H_0: \mu_1 = \mu_2$ vs $H_\alpha : \mu_1 \neq \mu_2$
- We will reject the Null hypothesis $H_0: \mu_1 = \mu_2$ if and only if $|T| \gt t_{1-\alpha/2, df}$, where the T-test statistics value exceeds the critical value 
- $CriticalValue = t_{1-\alpha/2, df} = t_{0.975, 25} = qt(0.975, df=25) = 2.059539$ 
- $\overline{X} - \overline{Y} = t_{1-\alpha/2.df} \sqrt{\frac{(m - 1)\sigma_1^2 + (n - 1)\sigma_2^2}{m + n - 2}(\frac{1}{m}+\frac{1}{n})}$ 
- $T = \frac{\overline{X} - \overline{Y}}{\sqrt{\frac{(m - 1)\sigma_1^2 + (n - 1)\sigma_2^2}{m + n - 2}(\frac{1}{m}+\frac{1}{n})}} = \frac{10.26933 - 4.41}{\sqrt{\frac{(15 - 1)11.46239 + (12 - 1)29.94576}{15 + 12 - 2}(\frac{1}{15}+\frac{1}{12})}} = 3.41766025706$ 
```{r}
t = (group1Mean - group2Mean) / sqrt(((((group1Size - 1) * group1Var) + ((group2Size - 1) * group2Var))/ (group1Size + group2Size - 2)) * (1/group1Size + 1/group2Size))
t
```
- $|T| > t_{1-\alpha/2, df} \implies = |3.417662| > 2.059539 \implies True$
- Therefore, we reject the null hypothesis and conclude that the two population means are different at the 0.05 significance level.


## B) Assuming $\sigma_{1}^{2} \neq \sigma_{2}^{2}$ 
### i) Construct a 90% confidence interval for $\mu_1 - \mu_2$ and interpret
- Given $\sigma_{1}^{2} \neq \sigma_{2}^{2}$, therefore, we can assume df as follow:
- $df = \frac{(\frac{\sigma_1^2}{m} + \frac{\sigma_2^2}{n})^2}{\frac{(\frac{\sigma_1^2}{m})^2}{m - 1} + \frac{(\frac{\sigma_2^2}{n})^2}{n - 1}} = \frac{(\frac{11.46239}{15} + \frac{29.94576}{13})^2}{\frac{(\frac{11.46239}{15})^2}{15 - 1} + \frac{(\frac{29.94576}{12})^2}{15 - 1}} = 17.48036$
- Below is the Lower and Upper Confidence Limits equation for unequal-variance:
- $P(\overline{X} - \overline{Y} - Z_{\alpha/2} \sqrt{\frac{\sigma_{1}^2}{m} + \frac{\sigma_{2}^2}{n}} \lt \mu_1 - \mu_2 \lt \overline{Y} + Z_{\alpha/2} \sqrt{\frac{\sigma_{1}^2}{m} + \frac{\sigma_{2}^2}{n}})$
- $\mu_1 - \mu_2 = \overline{X} - \overline{Y} \pm t_{1 - \alpha/2,df} \sqrt{\frac{\sigma_{1}^2}{m} + \frac{\sigma_{2}^2}{n}}$
- $\mu_1 - \mu_2 = 10.26933 - 4.41 \pm 1.736861 \sqrt{\frac{11.46239}{15} + \frac{29.94576}{12}}$
- $\mu_1 - \mu_2 = (2.723523, 8.995144)$
```{r}
alpha = 0.10 / 2

numerator = ((group1Var/group1Size) + (group2Var/group2Size))**2
denominator = ((group1Var/group1Size)**2)/(group1Size - 1) + ((group2Var/group2Size)**2)/ (group2Size - 1)
dfSize = numerator / denominator

lower = group1Mean - group2Mean + qt(alpha,df=dfSize) * sqrt(group1Var/group1Size + group2Var/group2Size)
upper = group1Mean - group2Mean - qt(alpha,df=dfSize) * sqrt(group1Var/group1Size + group2Var/group2Size)

#t.test(Group1, Group2, conf.level = 0.90)

lower
upper

```
- From this, we can see that  $2.723523 \lt \mu_1 - \mu_2 \lt 8.995144$ 
- Therefore, we are highly confident that the true population from group 1 exceeds the true population from group2 by between 2.723523 - 8.995144 

### ii) At 10% level of significance, test $H_0: \mu_1 = \mu_2$ vs $H_\alpha : \mu_1 \neq \mu_2$
- We will reject the Null hypothesis $H_0: \mu_1 = \mu_2$ if and only if $T \gt t_{1-\alpha, df}$, where the T-test statistics value exceeds the critical value 
- $CriticalValue = t_{1-\alpha/2, df} = t_{0.90,  17.48036} = qt(0.90, df=17.48036) = 1.3319$ 
- $\overline{X} - \overline{Y} = t_{1 - \alpha/2,df} \sqrt{\frac{\sigma_{1}^2}{m} + \frac{\sigma_{2}^2}{n}}$ 
- $T = \frac{\overline{X} - \overline{Y}}{\sqrt{\frac{\sigma_{1}^2}{m} + \frac{\sigma_{2}^2}{n}}} = \frac{10.26933 - 4.41}{\sqrt{\frac{11.46239}{15} + \frac{29.94576}{12}}} = \frac{5.859333}{1.805447} = 3.245364$ 
```{r}
t = (group1Mean - group2Mean) / sqrt(group1Var/group1Size + group2Var/group2Size)
t
```
- $T > t_{1-\alpha, df} \implies = 3.245364 \gt 1.3319 \implies True$
- Therefore, we reject the null hypothesis and conclude that the two population means are different at the 0.10 significance level.












