---
title: "Q3"
author: "Huiyan Li"
date: "4/18/2020"
output: html_document
---

# Assignment 2: Question 3

```{r}
# Only change this following line, remove 261 and put your student id
student_id=1001145664
# do not change anything below
set.seed(student_id)
Group1= round(rnorm(15,mean=10,sd=4),2)
Group2= round(rnorm(12,mean=7,sd=4),2)
```

### A) Fit a least square regression line and calculate the intercept and the slope.
- $\overline{x} =  0.5555556$ \
- $\overline{y} =  7.665185$ \
- $\sum_{i=1}^{n}(x_i - \overline{x})(y_i - \overline{y}) = 39.06222$ \
- $\sum_{i=1}^{n}(x_i - \overline{x})^2 = 6.666667$ \
- $b_2 = \frac{\sum_{i=1}^{n}(x_i - \overline{x})(y_i - \overline{y})}{\sum_{i=1}^{n}(x_i - \overline{x})^2} = \frac{39.06222}{6.666667} = 5.859333$ \
- $b_1 = \overline{y} - b_{2}\overline{x} = 7.665185 - 5.859333 * 0.5555556 = 4.41$ \
- $y = 4.41 + 5.859333x$
```{r}
y=c(Group1,Group2)
x=c(rep(1,length(Group1)),rep(0,length(Group2)))
cbind(y,x)

b2 = sum((x-mean(x))*(y-mean(y))) / sum((x-mean(x))^2) 
b1 = mean(y) - b2 * mean(x)

b1
b2
```

### B) At 5% level of significance, test that the true slope parameter is zero
- $CriticalValue = t_{1-\alpha/2, df} = t_{0.975, 25} = qt(0.975, df=25) = 2.059539$ \
- $SE(B_2) = \sqrt{\frac{S^2}{\sum_{i=1}^{n}(x_i - \overline{x})^2}} = 1.714427$ \
- $B_2 = 5.859333$
- $T = \frac{B_2 - \beta_2}{\sqrt{\frac{S^2}{\sum_{i=1}^{n}(x_i - \overline{x})^2}}} = \frac{5.859333 - 0}{1.714427} = 3.417663$
```{r}
y_pred = 4.41 + 5.859333*x
df = length(Group1) + length(Group2) - 2
S2 = sum((y-y_pred)^2)/df
SE_B2 = sqrt(S2/sum((x-mean(x))^2))
SE_B2

testStatistic = b2 / SE_B2
testStatistic
```
From our calculation, we see that the the test statistic is 3.417662, which is greater than the critical value of 2.05953.\
Therefore, we reject the null hypothesis $H_0: \beta_2 = 0$

### C) Match your answer from part (b) to your answers from Question 2. Describe briefly any similarity that you see.
- We see that the level of significance, critical value, and the test statistic are identical in both Q2 part A, ii and Q3 part b.
- Which indicates there is a equal correlationship between true slope parameter and the true mean.










