---
title: "Q2"
author: "Huiyan Li"
date: "3/29/2020"
output: html_document
---

### **Using for loop to find all combination from this population with replacement and sample size of n = 3**
```{r}
# Calculate the 125 combination of the population possible
combination_list = vector()
for (valA in c(21:25)) {
  for (valB in c(21:25)) {
    for (valC in c(21:25)) {
      combination_list <- c(combination_list, c(valA, valB, valC))
    }
  }
}
combination_list <- matrix(combination_list, ncol = 3, byrow=TRUE) 
colnames(combination_list) <-  c("Col1", "Col2", "Col3")
```

Given that in the assignment hand out, the equation is using $X_{i} - \overline{X}$ \
Therefore, I am assuming $\overline{X}$ is referring to the sample mean of the combination list\
As we don't know the actual global mean $\mu$ \
```{r}
sample_mean = mean(combination_list)
sample_variance_list = vector()
sigma_variance_list = vector()
for (row in 1:nrow(combination_list)) {
  sample = c(combination_list[row, 0:3])
  
  # Compute the sample variances using the first equation
  sample_variance = sum((sample - mean(sample))**2)/2
  sample_variance_list <- c(sample_variance_list, sample_variance)

  # Compute the sample variances using the second equation
  sigma_variance = sum((sample - mean(sample))**2)/3
  sigma_variance_list <- c(sigma_variance_list, sigma_variance)
}
```

```{r}
s = sample_variance_list
s
```

```{r}
sigma = sigma_variance_list
sigma
```

### **A. By calculating $Bias[S^{2}]$ and $Bias[\hat{\sigma^{2}}]$ check the unbiasedness of these two estimators**

We know that the population variance is 2 given from the assigment\
$Bias[S^{2}] = E(S^{2}) - S^{2}$ \
$Bias[S^{2}] = E(\overline{S^{2}}) - S^{2}$ \
$Bias[S^{2}] = E(mean(S^{2})) - S^{2}$ \
$Bias[S^{2}] = mean(S^{2}) - S^{2}$ \
$Bias[S^{2}] = mean(S^{2}) - 2$ \
```{r}
# Given from the assignment
population_variance = 2
s_bias = mean(s) - population_variance
s_bias
```

Simiarly for $Bias[\sigma^{2}]$ \
$Bias[\sigma^{2}] = E(\sigma^{2}) - \sigma^{2}$ \
$Bias[\sigma^{2}] = E(\overline{\sigma^{2}}) - \sigma^{2}$ \
$Bias[\sigma^{2}] = E(mean(\sigma^{2})) - \sigma^{2}$ \
$Bias[\sigma^{2}] = mean(\sigma^{2}) - \sigma^{2}$ \
$Bias[\sigma^{2}] = mean(\sigma^{2}) - 2$ \
```{r}
# Given from the assignment
population_variance = 2
sigma_bias = mean(sigma) - population_variance
sigma_bias
```

From this, we can conclude that the $S^{2}$ is bias, and the $\sigma^{2}$ is not bias. 


### **B. By calculating all three components separately check the following identity**
Given the equation, $MSE[\hat{\sigma^{2}}] = var[\hat{\sigma^{2}}] + (Bias[\hat{\sigma^{2}}])^{2}$ \
$var[\hat{\sigma^{2}}]$ \
```{r}
# Given from the assignment
population_variance = 2
sigma_variance = sum((sigma - population_variance)**2)/125  
sigma_variance
```

$Bias[\hat{\sigma^{2}}]^{2}$ \
```{r}
sigma_bias_square = sigma_bias**2
sigma_bias_square
```

$MSE[\hat{\sigma^{2}}]$ \
```{r}
mse = sigma_variance + sigma_bias_square
mse
```
Knowing that $Bias[\hat{\sigma^{2}}]^{2} = 0$, implies $MSE[\hat{\sigma^{2}}] = var[\hat{\sigma^{2}}]$ \
Which decreases as N (sample size) increases, we can conclude MSE is consistent
























